### 2023-03-18 notebooks/fidelity.qmd
differentiable penalties for fidelity and plausibility

```{julia}
# Setup
counterfactual_data = load_multi_class()
M = fit_model(counterfactual_data, :MLP)
target = 4
factual = 2
chosen = rand(findall(predict_label(M, counterfactual_data) .== factual))
x = select_factual(counterfactual_data, chosen)

@@

```{julia}
@objective(generator, _ + 0.1distance_l2 + 100.0distance_from_energy)
ce = generate_counterfactual(x, target, counterfactual_data, M, generator)
p2 = plot(ce)
```

>>>>

## Binary

```{julia}
# Setup
counterfactual_data = load_linearly_separable()
M = fit_model(counterfactual_data, :DeepEnsemble)
target = 2
factual = 1
chosen = rand(findall(predict_label(M, counterfactual_data) .== factual))
x = select_factual(counterfactual_data, chosen)

## Multi-Class

```{julia}
# Setup
counterfactual_data = load_multi_class()
M = fit_model(counterfactual_data, :DeepEnsemble)
target = 4
factual = 2
chosen = rand(findall(predict_label(M, counterfactual_data) .== factual))
x = select_factual(counterfactual_data, chosen)

@@

```{julia}
using CCE: distance_from_energy
@objective(generator, _ + 0.1distance_l2 + 10.0distance_from_energy)
ce = generate_counterfactual(x, target, counterfactual_data, M, generator)
p2 = plot(ce)
```

```{julia}
using CCE: distance_from_targets
@objective(
    generator, 
    _ + 0.1distance_l2 + 1.0distance_from_energy + 10.0distance_from_targets
)
ce = generate_counterfactual(x, target, counterfactual_data, M, generator)
p3 = plot(ce)
```
